Comparison of CORD-19-trained GPT-2-based Chatbot Responses Across Different Text Semantic Similarity Approaches

### 2020-04-11 paper/paper.tex
Fix incomplete questions and update the paper

\section{Questions}

For evaluating the performance of the approaches, we have chose 12 different
questions. For each approach, we generated 5 different answers for the same
question, resulting in the total of 240 answers. We then asked experienced
medical personnel at Mayo Clinic to rate these answers. The questions are
presented below.

>>>>

\section{Questions and Evaluation}

For evaluating the performance of the approaches, we chose 12 different
questions. For each approach, we generated 5 different answers for the same
question, resulting in the total of 240 answers. We then asked experienced
medical personnel at Mayo Clinic to rate these answers. The questions are
presented below.

\begin{itemize}
  \item Are there geographic variations in the mortality rate of COVID-19?
  \item What is known about transmission, incubation, and environmental stability of COVID-19?
  \item Is there any evidence to suggest geographic based virus mutations of COVID-19?
  \item Are there geographic variations in the rate of COVID-19 spread?
  \item What do we know about virus genetics, origin, and evolution of COVID-19?
  \item What has been published about ethical and social science considerations of COVID-19?
  \item What has been published about medical care of COVID-19?
  \item What do we know about diagnostics and surveillance of COVID-19?
  \item What do we know about COVID-19 risk factors?
  \item What has been published about information sharing and inter-sectoral collaboration of COVID-19?
  \item What do we know about vaccines and therapeutics of COVID-19?
  \item What do we know about non-pharmaceutical interventions of COVID-19?
\end{itemize}
